Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-14 implementation/implementation.tex
New figure
New fig and table

    [what is factor]

    [what is adaptive distance]

@@

[FIGURE here]

@@

However considering the result after 20 generation (FIGURE), the resultant model gives the contrary preference. Applying factors and using adaptive distance can lead the resultant model less accurate (after the same generation iterations): they have wider inter-quantile range and may requires more generations to converge.

@@

@@

>>>>

% [what is factor]

% [what is adaptive distance]

@@

% [FIGURE here]

\begin{figure}[ht]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/ib.png}}
    \end{center}

    \caption[Factors and adaptive distance experiments]%
    {Factors and adaptive distance experiments. Left: Total required samples. Right: acceptance rates in each generation}
    \label{fig:factor}

    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/ib_factor.png}}
    \end{center}

    \caption[CAPTION]%
    {DESCRIBE}
    \label{fig:factor_sim}

@@

However considering the result after 20 generation (FIGURE), the resultant model gives the contrary preference. Applying factors and using adaptive distance can lead the resultant model less accurate (after the same generation iterations): they have wider inter-quantile range and may requires more generations to converge. TODO

@@

\begin{figure}[ht]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/model5_para.png}}
    \end{center}

    \caption[Estimated posterior distribution of parameters in model 5]%
    {Estimated posterior distribution of parameters in model 5. Shaded range indicates 25\%--75\% quantile of the population}
    \label{fig:model5_para}

\begin{figure}[ht]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/inferno5.png}}
    \end{center}
    \caption[Joint density distribution of each parameter pair]%
    {Joint distribution of each parameter pair. MORE DESCRIPTION}
    \label{fig:model5_para_joint}
\end{figure}

@@

\begin{table}[t!]
    \centering
    \begin{tabular}{|c c c|}
        \hline
        Parameter            & Mean value & Inter-quartile interval \\[0.5ex]
        \hline\hline
        $\lambda_N$          & 13.5       & [12.9, 14.2]            \\
        $a$                  & 0.0175     & [0.0145, 0.0207]        \\
        $\kappa_{N\beta}$    & 0.176      & [0.109, 0.234]          \\
        $\mu_N$              & 0.0239     & [0.0113, 0.0332]        \\
        $\nu_{N\Phi}$        & 0.125      & [0.115, 0.134]          \\
        \hline
        $\kappa_{\Phi\beta}$ & 0.123      & [0.115, 0.131]          \\
        $\mu_\Phi$           & 0.0234     & [0.0199, 0.0267]        \\
        \hline
        $s_{\beta N}$        & 2.38       & [2.02, 2.73]            \\
        $\mu_\beta$          & 2.67       & [2.24, 3.10]            \\
        \hline
        $s_{\alpha\Phi}$     & 0.574      & [0.295, 0.786]          \\
        $\mu_\alpha$         & 8.91       & [6.07, 11.1]            \\
        $f_{\beta\alpha}$    & 0.577      & [0.361, 0.738]          \\
        \hline
    \end{tabular}
    \caption[Estimated parameter values of model 3]
    {Estimated parameter values of model 3, using uniform prior distribution and log-uniform prior distribution respectively}
    \label{table:estimated5}
\end{table}
